Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-14 paper.tex
move remark on gridsearchcv after the snippet

From an API point of view, cross-validation schemes are given as iterator
objects over train and test folds on the training data. The library provides
various such iterators, including K-Fold, Leave-One-Out or shuffled
cross-validation schemes. The score function used by default is the function
provided by the estimator itself. However, the library provides a variety of
score functions that can be used instead, including -- among many others --
accuracy, AUC or $F_\beta$-score for classifiers; $R^2$ score or mean squared
error for regressors; or the Rand Index for clustering estimators. Also, let us
note that \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} instances are
themselves estimators. In particular, they provide \texttt{predict},
\texttt{predict\_proba}, \texttt{transform} and \texttt{score} methods that are
all transparently delegated to the best estimator found during \texttt{fit}.

@@

    clf = GridSearchCV(SVC(), param_grid, scoring="roc_auc", cv=10)
    clf.fit(X_train, y_train)
\end{verbatim}

>>>>

From an API point of view, cross-validation schemes are given as iterator
objects over train and test folds on the training data. The library provides
various such iterators, including K-Fold, Leave-One-Out or shuffled
cross-validation schemes. The score function used by default is the function
provided by the estimator itself. However, the library provides a variety of
score functions that can be used instead, including -- among many others --
accuracy, AUC or $F_\beta$-score for classifiers; $R^2$ score or mean squared
error for regressors; or the Rand Index for clustering estimators.

@@

    clf = GridSearchCV(SVC(), param_grid, scoring="roc_auc", cv=10)
    clf.fit(X_train, y_train)
    y_pred = clf.predict(X_test)
\end{verbatim}
Let us finally note \texttt{GridSearchCV} and \texttt{RandomizedSearchCV}
instances are themselves estimators. In particular, they provide
\texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and \texttt{score}
methods that are all transparently delegated to the best estimator found during
\texttt{fit}, as the example shows.
